% Appendix A: Expanded User Manual (Extraordinary Expansion)
\chapter{USER MANUAL: NEBULA COMMAND CENTER}

This manual provides a step-by-step guide for setting up and using the Nebula Multi-Cloud platform. It includes separate sections for Windows, macOS, and Linux setup.

\section{System Dependencies and OS-Specific Setup}

\subsection{Phase 1-A: Windows Setup (WSL2 Highly Recommended)}
For Windows users, using the Windows Subsystem for Linux (WSL2) with Ubuntu 22.04 LTS is the most stable and performant environment for Nebula.
1) \textbf{Enable WSL2}: Open PowerShell as Administrator and run: \texttt{wsl --install}.
2) \textbf{Docker Desktop}: Install Docker Desktop and enable the WSL2 backend in the settings.
3) \textbf{Terraform}: Install using the Linux distribution's \texttt{apt-get} to ensure it matches the production worker environment.

\subsection{Phase 1-B: macOS Setup (Homebrew Oriented)}
macOS provides a robust Unix-based environment that is excellent for development.
1) \textbf{Install Homebrew}: \texttt{/bin/bash -c "$(curl -fsSL https://raw.githubusercontent.com/Homebrew/install/HEAD/install.sh)"}
2) \textbf{Docker Desktop for Mac}: Download and install the DMG for Apple Silicon or Intel as appropriate.
3) \textbf{Terraform via Brew}: Run \texttt{brew install terraform} to get the latest binary.

\subsection{Phase 1-C: Linux Setup (Native Deployment)}
Native Linux (Ubuntu 22.04+) is the preferred environment for the production Nebula worker cluster.
1) \textbf{Install Docker}: \texttt{sudo apt-get install docker.io docker-compose}.
2) \textbf{Terraform via Hashicorp Repo}: 
   - Add the HashiCorp GPG key.
   - Add the HashiCorp repository.
   - \texttt{sudo apt-get update && sudo apt-get install terraform}.
3) \textbf{Python 3.11}: Ensure Python 3.11 and the \texttt{venv} module are installed for isolated virtual environments.

\section{Local Backend Installation Guide}

\subsection{Phase 2: Environment Configuration}
Create a \texttt{.env} file in the backend directory with the following variables:
\begin{lstlisting}[language=XML]
DATABASE_URL=postgresql://user:pass@localhost:5432/nebula_db
SECRET_KEY=yoursymmetricsecretkeyhere
REDIS_URL=redis://localhost:6379/0
AI_COPILOT_API_KEY=youropenaikeyhere
\end{lstlisting}

\subsection{Phase 3: Service Startup}
Use the provided \texttt{docker-compose.yml} to start the peripheral services:
\begin{lstlisting}[language=SQL]
docker-compose up -d db redis
\end{lstlisting}
This will launch PostgreSQL and Redis in the background, allowing the FastAPI and Celery processes to connect immediately.

\section{Cloud Provider Configuration}

\subsection{Registering AWS Credentials}
1) Go to the AWS Console -> IAM -> Users.
2) Create a user with \texttt{Programmatic Access} and \texttt{AdministratorAccess}.
3) Copy the \texttt{Access Key ID} and \texttt{Secret Access Key}.
4) In Nebula, go to "Settings" -> "Add Provider" and select "AWS."
5) Paste your keys and click "Securely Register."

\subsection{Registering Azure Credentials}
Azure requires a Service Principal for programmatic access.
1) Open Azure CLI and run: \texttt{az ad sp create-for-rbac --name Nebula}.
2) Capture the \texttt{appId}, \texttt{password}, and \texttt{tenantId}.
3) In Nebula, go to "Add Provider" and select "Azure."
4) Enter the credentials to enable Azure VM/Storage provisioning.

\subsection{Registering GCP Credentials}
Google Cloud onboarding requires a service account with a JSON key and the correct project scope.
1) Open the Google Cloud Console and create or select a project.
2) Navigate to IAM and Admin -> Service Accounts.
3) Create a service account with the minimum roles required for the resources you plan to manage.
4) Generate a JSON key and store it securely.
5) In Nebula, choose "Add Provider" -> "GCP" and upload or paste the service account fields.
6) Confirm the project ID and default region before saving the credential.

\subsection{Environment Variable Reference}
\begin{table}[H]
\centering
\caption{Essential Environment Variables for Local Setup}
\label{tab:appendix_env_vars}
\begin{tabular}{|p{3.2cm}|p{3.2cm}|p{4.8cm}|}
\hline
\textbf{Variable} & \textbf{Example} & \textbf{Purpose} \\ \hline
DATABASE\_URL & postgresql://user:pass@localhost:5432/nebula\_db & database connection string \\ \hline
REDIS\_URL & redis://localhost:6379/0 & queue broker and task transport \\ \hline
SECRET\_KEY & generated fernet key & encryption of provider secrets \\ \hline
AI\_COPILOT\_API\_KEY & provider token & failure analysis integration \\ \hline
LOG\_LEVEL & info & runtime verbosity tuning \\ \hline
\end{tabular}
\end{table}

\section{Using the Nebula Dashboard}

\subsection{Provisioning Your First Resource}
1) Click the "+" icon in the top right corner.
2) Select your cloud provider (e.g., AWS).
3) Select "Virtual Machine" from the resource dropdown.
4) Enter a name (e.g., "my-dev-vm") and select "t3.micro."
5) Click "Launch Infrastructure" and watch the real-time logs in the "Cockpit" panel.

\subsection{Recommended First-Day Validation}
Before using live cloud accounts heavily, perform a short validation cycle:
\begin{enumerate}
    \item create a test credential for one provider,
    \item launch a low-cost resource in a sandbox region,
    \item confirm that the task reaches the completed state,
    \item verify that the resource appears in the inventory list,
    \item trigger a manual sync and confirm metadata remains consistent,
    \item delete the test resource and verify that cleanup completes successfully.
\end{enumerate}
This sequence confirms that the core path of credential storage, background execution, Terraform generation, sync, and deletion is functioning correctly.

\subsection{Daily Operator Workflow}
An operator using Nebula in a lab or project environment can follow a simple day-to-day routine:
\begin{enumerate}
    \item review the dashboard counters for pending or failed tasks,
    \item check whether any provider credentials are expired or misconfigured,
    \item launch or modify resources as needed for current work,
    \item monitor logs during provisioning and investigate slow tasks,
    \item run a synchronization cycle before generating reports or screenshots,
    \item remove unused resources to avoid cost drift.
\end{enumerate}

\subsection{Cleanup Procedure}
To clean up a project safely:
\begin{enumerate}
    \item filter the resource table by project or tag,
    \item delete non-critical compute resources first,
    \item remove dependent storage or network objects only after confirming no tasks are active,
    \item run a final sync to detect drift or residual assets,
    \item archive logs if the environment is part of a graded evaluation or experiment.
\end{enumerate}

\section{Troubleshooting and FAQs}

\subsection{Common Issues and Remediation}
\begin{itemize}
    \item \textbf{Issue}: "PostgreSQL connection refused."
    \item \textbf{Solution}: Ensure the Docker container for the DB is running and the port mapping \texttt{5432:5432} is correct.
    \item \textbf{Issue}: "Terraform state locked."
    \item \textbf{Solution}: Delete the \texttt{.terraform.tfstate.lock.info} file in the workspace directory and retry.
    \item \textbf{Issue}: "Azure subscription not found."
    \item \textbf{Solution}: Verify the Tenant ID and ensure the Service Principal has \texttt{Contributor} permissions on the subscription.
\end{itemize}

\subsection{Expanded Troubleshooting Matrix}
\begin{table}[H]
\centering
\caption{Common Operational Issues and Recovery Actions}
\label{tab:appendix_troubleshooting}
\begin{tabular}{|p{3.4cm}|p{3.4cm}|p{4.2cm}|}
\hline
\textbf{Symptom} & \textbf{Likely Cause} & \textbf{Recommended Action} \\ \hline
Task remains queued & worker offline or broker unavailable & restart worker service and verify Redis connectivity \\ \hline
Logs stop midway & Terraform process stalled or provider timeout & inspect worker logs and retry with lower concurrency \\ \hline
Sync returns partial inventory & permission scope too narrow & validate provider role and region scope \\ \hline
AI analysis unavailable & missing API key or rate limit & verify key configuration and retry later \\ \hline
Repeated auth failures & expired credential or wrong secret format & re-register provider credential and test read access \\ \hline
\end{tabular}
\end{table}

\subsection{Frequently Asked Questions}
\begin{enumerate}
    \item \textbf{Can Nebula manage multiple accounts of the same provider?}
    Yes. The credential vault can store multiple provider entries, provided each is tagged and scoped clearly.
    \item \textbf{Should production credentials be used during development?}
    No. Use sandbox or low-privilege accounts whenever possible.
    \item \textbf{Why does a task take longer than the API request?}
    Because the API only records intent and queues the work. The actual infrastructure execution happens asynchronously in the worker layer.
    \item \textbf{What should I do if a resource is visible in the cloud console but missing in Nebula?}
    Trigger a manual synchronization cycle. If the resource still does not appear, verify whether the credential used by Nebula has permission to list that resource type.
\end{enumerate}

\newpage
