% BIBLIOGRAPHY (Standard LaTeX format for numeric citations)
\chapter*{BIBLIOGRAPHY}
\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}

\begin{thebibliography}{99}

    \bibitem{mell2011nist} Mell, Peter and Grance, Timothy. "The NIST Definition of Cloud Computing," \textit{NIST Special Publication 800-145}, 2011.

    \bibitem{brikman2019terraform} Brikman, Yevgeniy. \textit{Terraform: Up \& Running: Writing Infrastructure as Code}, O'Reilly Media, 2019.

    \bibitem{armbrust2010view} Armbrust, Michael, et al. "A view of cloud computing," \textit{Communications of the ACM}, Vol. 53, No. 4, pp. 50-58, 2010.

    \bibitem{buyya2009vision} Buyya, Rajkumar, et al. "Cloud computing and emerging IT platforms: Vision, hype, and reality for delivering computing as the 5th utility," \textit{Future Generation computer systems}, Vol. 25, No. 6, pp. 599-616, 2009.

    \bibitem{morris2016iac} Morris, Kief. \textit{Infrastructure as Code: Managing Servers in the Cloud}, O'Reilly Media, 2016.

    \bibitem{aldhuraibi2018elasticity} Al-Dhuraibi, Yahya, et al. "Elasticity in cloud computing: state of the art and research challenges," \textit{IEEE Transactions on Services Computing}, Vol. 11, No. 2, pp. 430-447, 2018.

    \bibitem{grozev2014survey} Grozev, Nikolay and Buyya, Rajkumar. "Inter-Cloud architectures and application brokering: taxonomy and survey," \textit{Software: Practice and Experience}, Vol. 44, No. 3, pp. 369-390, 2014.

    \bibitem{zhang2010survey} Zhang, Qi, et al. "Cloud computing: state-of-the-art and research challenges," \textit{Journal of Internet Services and Applications}, Vol. 1, No. 1, pp. 7-18, 2010.

    \bibitem{toosi2014survey} Toosi, Adel Nadjaran, et al. "Interconnected cloud computing environments: Challenges, taxonomy, and survey," \textit{ACM Computing Surveys (CSUR)}, Vol. 47, No. 1, pp. 1-47, 2014.

    \bibitem{bernstein2009intercloud} Bernstein, David, et al. "Inter-cloud computing," \textit{2009 IEEE International Conference on Cloud Computing}, IEEE, pp. 74-80, 2009.

    \bibitem{polamarasetti2025ai} Polamarasetti, Shalini, et al. "Enhancing Strategic Business Decisions with AI-Powered Forecasting Models," \textit{ASSIC 2025}, IEEE, 2025.

    \bibitem{hashicorp2024terraform} HashiCorp. "Terraform Documentation and Architecture," 2024. [Online]. Available: https://developer.hashicorp.com/terraform

    \bibitem{react_docs_2026} Meta Open Source. "React Documentation," 2026. [Online]. Available: https://react.dev

    \bibitem{fastapi_docs_2026} FastAPI Project. "FastAPI Documentation," 2026. [Online]. Available: https://fastapi.tiangolo.com

    \bibitem{redis_docs_2026} Redis Ltd. "Redis Documentation," 2026. [Online]. Available: https://redis.io/docs/

    \bibitem{docker_docs_2026} Docker Inc. "Docker Documentation," 2026. [Online]. Available: https://docs.docker.com/

    \bibitem{boto3_docs_2026} Amazon Web Services. "Boto3 Documentation," 2026. [Online]. Available: https://boto3.amazonaws.com

    \bibitem{anthos_docs_2024} Google Cloud. "Anthos Overview," 2024. [Online]. Available: https://cloud.google.com/anthos

    \bibitem{beloglazov2012energy} Beloglazov, Anton, et al. "Energy-aware resource allocation heuristics for efficient management of data centers," \textit{Future Generation Computer Systems}, Vol. 28, No. 5, pp. 755-768, 2012.

    \bibitem{calheiros2011cloudsim} Calheiros, Rodrigo N, et al. "CloudSim: a toolkit for modeling and simulation of cloud computing environments," \textit{Software: Practice and Experience}, Vol. 41, No. 1, pp. 23-50, 2011.

    \bibitem{vaquero2008break} Vaquero, Luis M, et al. "A break in the clouds: towards a cloud definition," \textit{ACM SIGCOMM Computer Communication Review}, Vol. 39, No. 1, pp. 50-55, 2008.

    \bibitem{singh2016survey} Singh, Sukhpal and Chana, Inderveer. "A Survey of Cloud Resource Management," \textit{ACM Computing Surveys}, Vol. 48, No. 3, pp. 1-39, 2016.

    \bibitem{celery_docs_2024} Celery Project. "Celery: Distributed Task Queue," 2024. [Online]. Available: https://docs.celeryq.dev

    \bibitem{sentinel_docs_2024} HashiCorp. "Terraform Sentinel: Policy as Code for Infrastructure," 2024. [Online]. Available: https://www.hashicorp.com/products/terraform/sentinel

    \bibitem{villari2016intercloud} Villari, Massimo, et al. "Leveraging the Intercloud," \textit{IEEE Cloud Computing}, Vol. 3, No. 1, pp. 31-38, 2016.

    \bibitem{rahman2020iac} Rahman, Akond, et al. "The 5 W’s of Infrastructure as Code: A Case Study," \textit{2020 IEEE/ACM 42nd ICSE-SEIP}, IEEE, pp. 71-80, 2020.

    \bibitem{bessani2011depsky} Bessani, Alysson, et al. "DepSky: Dependable and Secure Storage in a Cloud-of-Clouds," \textit{ACM EuroSys Conference}, 2011.

    \bibitem{villari2013discovery} Villari, Massimo, et al. "Enabling Resource Discovery and Mapping in the Intercloud," \textit{2013 IEEE SOSE}, IEEE, pp. 115-120, 2013.

    \bibitem{ieee830} IEEE Computer Society, "IEEE Recommended Practice for Software Requirements Specifications," \textit{IEEE Std 830-1998}, 1998.

    \bibitem{pydantic_docs} Pydantic Project, "Pydantic Documentation: Data validation and settings management using Python type hints," 2024. [Online]. Available: https://pydantic-docs.helpmanual.io

\end{thebibliography}

