% Chapter 11: DevOps Pipeline and Release Engineering
\chapter{DEVOPS PIPELINE AND RELEASE ENGINEERING}
\thispagestyle{plain}

In addition to being a piece of software, Nebula also constitutes a way of deploying the software. As such, the surrounding DevOps pipeline falls within the technical scope of the project. The infrastructure manager that governs multiple clouds also needs to be deployed through a reliable, reproducible, and low-risk release cycle. This chapter discusses the release engineering principles behind that endeavor.

\section{Source Control and Branching Strategy}
Code management benefits greatly from a branching policy that distinguishes development and release activities. An efficient structure consists of:

\begin{itemize}
    \item \textbf{main}: branch for production releases with merge protection,
    \item \textbf{develop}: branch for integrating finished features,
    \item \textbf{feature/*}: task-specific branches,
    \item \textbf{hotfix/*}: emergency fixes for critical production problems.
\end{itemize}


The strategy minimizes risk during the release cycle by making it possible to review infrastructure changes, frontend changes, and backend changes simultaneously prior to deploying into a shared environment. Traceability is ensured since each release can be traced to its source code, pull requests, and approvals.

\section{Build Artifacts and Versioning}
Nebula creates several artifacts ready for deployment:

\begin{enumerate}
    \item frontend static resources,
    \item backend API service image,
    \item worker container image,
    \item Terraform module template and shared configuration bundle, 
    \items database migrations scripts.
    \item database migration scripts.
\end{enumerate}

All these elements need to be released under consistent versioning using a specific tag, such as \texttt{v1.4.0}. The important point here is to align the versions of the API service image, worker service image, and the database migration status against the same release. Otherwise, the debugging process will become unnecessarily complex because various elements may be based on conflicting assumptions.

\section{Continuous Integration Stages}
The CI process serves as the first filter for ensuring software quality. In its minimal implementation, the continuous integration tool should run:

\begin{itemize}
    \item backend static analysis and unit testing,
    \item frontend linting and build verification,
    \item syntax validation of Terraform templates,
    \item migration schema validation,
    \item API contract or smoke test.
\end{itemize}


The interesting aspect of this approach is that Terraform templates are considered as code artifacts. Although both the backend services and front end applications have passed all necessary tests, incorrectly structured Terraform template can make the entire platform unusable. Thus, the IaC layer must be tested along with the application layer.

\subsection{Illustrative Pipeline Definition}
\begin{lstlisting}[language=Python, caption=Representative CI Pipeline Skeleton]
stages:
  - validate
  - test
  - package
  - deploy

validate_backend:
  stage: validate
  script:
    - python -m pytest tests/unit

validate_frontend:
  stage: validate
  script:
    - npm ci
    - npm run build

validate_iac:
  stage: validate
  script:
    - terraform fmt -check
    - terraform validate

package_api:
  stage: package
  script:
    - docker build -t nebula-api:$CI_COMMIT_TAG backend

package_worker:
  stage: package
  script:
    - docker build -t nebula-worker:$CI_COMMIT_TAG backend
\end{lstlisting}

\section{Environment Promotion Workflow}
Releases must advance from environments that are less risky to more risky. The typical approach is to:

It is critical that releases advance like this because it is possible for multi-cloud control plane releases to have issues that regular unit tests will not discover. This is because when deploying, problems may arise during the following scenarios:

\begin{enumerate}
    \item merge reviewed code into the integration branch,
    \item automatically deploy to a shared test environment,
    \item run smoke tests on login, queuing, and provider connection,
    \item deploy the same artifact to the staging environment,
    \item approving deployment to production,
    \item closely watch early metrics after deploying to production.
\end{enumerate}

This progression matters because a multi-cloud control plane can fail in subtle ways that ordinary unit tests do not catch. A release may look healthy until it attempts provider authentication, state reconciliation, or asynchronous task execution with live infrastructure APIs. Promotion through increasingly realistic environments is therefore a core risk-reduction strategy.

\section{Secrets and Configuration Management}
The release pipeline should know how to separate code from environment-dependent sensitive data. The following list contains items that should never be kept in source control:


The release pipeline must distinguish between code and environment-specific secret material. The following items should never be embedded in source control:
\begin{itemize}
    \item master encryption keys,
    \item production database credentials,
    \item service principal password,
    \item third-party API tokens.
\end{itemize}


These configuration parameters should be injected at runtime via environmen- tal variables or secret management systems. This will help with secure rotation, minimize risk of leakage and maintain portability of the codebase across environments.

\section{Containerization Strategy}
Containerization will bring value to the Nebula application since it will guaran- tee consistent execution environment. API, workers, databases, and brokers are composable components that can be reproduced by developers on their local environments. Benefits include:

\begin{itemize}
    \item consistent runtime dependencies,
    \item easy onboarding process,
    \item versioned artifact deployments,
    \item defined boundaries of services,
    \item rollback mechanism to known good versions.
\end{itemize}


Containerization is not enough to ensure operational reliability. Container images require additional review of vulnerabilities, health checks, startup probes, and proper logging. It is particularly critical for the worker container which uses secrets and manages the execution of Terraform.

\section{Database Migration Discipline}
Migration of schemas is another frequent cause of fragile releases. Nebula holds information about users, credentials, tasks, and resource states; an irresponsible migration could impact security and availability. In such a case, a well-thought-out migration strategy should consider:

\begin{enumerate}
    \item migrating forward only when possible,
    \item reviewing nullable-to-non-nullable changes explicitly,
    \item performing data backfills as release steps,
    \item backing up data before any destructive migration steps,
    \item conducting smoke tests on the migrated schema.
\end{enumerate}

\section{Rollback Strategy}
Each part of a release has its rollback strategies:



\begin{itemize}
    \item \textbf{API code rollback}: rdeploying previous versions of API and worker images. 
    \item \textbf{Configuration rollback}: reverting to proven configurations and feature flags.
    \item \textbf{Infrastructure rollback}: mplementing reverse changes from a thorough review, not assuming immediate cloud infrastructure rollback.
\end{itemize}


The difference between the three kinds of rollback is important since it might be that the release failed in one domain but succeeded in others. For instance, the API code is stable enough to be rolled back, whereas the database schema still supports backward compatibility.


\section{Release Readiness Checklist}
\begin{table}
\centering
\caption{Release Gate Criteria}
\label{tab:release_gate}
\begin{tabular}{|p{4.0cm}|p{2.2cm}|p{5.0cm}|}
\hline
\textbf{Check} & \textbf{Required} & \textbf{Rationale} \\ \hline
Unit and integration tests pass & Yes & baseline quality signal \\ \hline
Terraform templates validate & Yes & prevents broken provisioning flows \\ \hline
Migration reviewed and backed up & Yes & protects persistent state \\ \hline
Secrets resolved in target environment & Yes & avoids startup and runtime failures \\ \hline
Staging smoke test completed & Yes & confirms end-to-end functionality \\ \hline
Operational owner assigned & Yes & ensures release accountability \\ \hline
Rollback note prepared & Recommended & accelerates incident response \\ \hline
\end{tabular}
\end{table}

\section{Discussion}
DevOps pipeline is no different from any other element that comprises the product itself; this element constitutes an integral part of the reliability envelope of the product. The idea behind Nebula is to decrease the complexity associated with operations for the sake of its users. For the same reason, the development team needs to practice discipline while building the very platform itself by applying such measures as versioning of artifacts, validation of infrastructure templates, use of secrets management outside the source code, and release promotion across multiple stages.

\newpage


% Chapter 12: Use Cases, Case Studies, and Cost Scenarios
\chapter{USE CASES, CASE STUDIES, AND COST SCENARIOS}
\thispagestyle{plain}

Multi-cloud orchestration becomes more valuable when assessed in terms of practical use case applications. This chapter will present several representative examples to highlight how Nebula can be used for various needs. There are no claims about universality and perfection made, instead, it aims to illustrate the power of a unified control plane as an abstraction for decision-making, deployment choices, and financial considerations.

\section{Use Case 1: Startup SaaS Platform}


Assume a startup working on customer-facing SaaS product and having a small engineer- ing group. The goal is to develop the solution fast and clearly, minimize upfront costs, and refrain from getting hooked up with one specific cloud provider for now. 


In such a situation, Nebula can assist with experimentation by offering a standardized interface for developing VMs, object stores, regional instances, etc. Instead of having to get used to all three portals immediately, the company will be able to make standardized requests and compare results side-by-side.


The key value here is cognitive efficiency. The engineering team is typically small and consists of people who both implement the solution and provide the corresponding infrastructure. Nebula will help reduce cognitive load, facilitate onboarding, and retain knowledge of what was deployed where and why.


For this type of organization, the main benefit is cognitive efficiency. The team is usually small, and the same engineers often handle both product features and infrastructure work. Nebula reduces context switching, shortens onboarding time for new team members, and preserves a record of what was provisioned and why.

\section{Use Case 2: Enterprise Department With Microsoft Alignment}


Assume an enterprise department that heavily utilizes Microsoft-related services for their identity and collaboration needs but wants certain analytics or external-facing solutions to be deployed in other clouds. For example, there might be an interest in leveraging AWS/GCP as opposed to Azure because the workload is better suited to particular providers. In such a scenario, Nebula can serve as a tool to keep Azure-based policy framework while still being able to manage other services in controlled manner.


In such an environment, multi-cloud orchestration is mostly about the policy-boundary nature as opposed to merely being convenient. The importance of onboarding, tag enfor- cing, restriction to regions, and auditability cannot be underestimated. However, having the same dashboard remains important because the department should know where resources are hosted regardless of the need for everyone to be proficient in each provider's console.
e.

\section{Use Case 3: Research Laboratory or Academic Institution}


Another scenario in which Nebula will work efficiently is when there are periodic demands for a computing cluster, storage facility, and reproducibility of the infrastructures for academic assignments or experiments. In such cases, budget visibility and repeatability will help since new people join the group and leave after some time, thereby making infrastructure information fragment among different groups of students.


The ability of Nebula to document, observe, and reuse workflows suits such scenarios well. This is because the control plane allows a technical lead to define a series of standardized procedures for setup and provide infrastructure templates for them to follow. Moreover, the technical leads will be able to see all the components and what has been set up using various providers.

\section{Use Case 4: Seasonal E-Commerce Expansion}


In the case where e-commerce sites experience seasonal demands, it might be desirable to maintain one cloud provider while being ready to use a second one in case the first one fails. In most times, not all resources will be used at any time depending on the level of activity. However, during high activity levels, it might be desirable to use the second cloud as well.


In such scenarios, the team must know how to distinguish between primary and backup resources, how resource inventory can be kept synchronized, and how faults can be analyzed quickly. This is one of the challenges the control plane can address by allowing task tracking and centralized inventory viewing.

\section{Illustrative Cost Scenario Comparison}
The following table provides an example of the kind of workload-based decision-making the control plane will allow. The numbers used in the table below are illustrative and not vendor quotes.

\begin{table}
\centering
\caption{Illustrative Cost and Fit Comparison by Scenario}
\label{tab:cost_scenario}
\begin{tabular}{|p{4.0cm}|p{2.0cm}|p{2.0cm}|p{3.0cm}|}
\hline
\textbf{Scenario} & \textbf{Primary Goal} & \textbf{Suggested Cloud Bias} & \textbf{Nebula Value} \\ \hline
Student development sandbox & low cost & burstable mixed cloud & one workflow for repeat setup \\ \hline
Enterprise internal app & identity alignment & Azure-first & governance and inventory unification \\ \hline
Data-heavy analytics prototype & fast experimentation & GCP-first & compare supporting infrastructure centrally \\ \hline
Broad service integration platform & service breadth & AWS-first & consistent provisioning and failure handling \\ \hline
Disaster recovery standby & resilience & dual-provider & coordinated fallback orchestration \\ \hline
\end{tabular}
\end{table}

\section{Case Study: Failed Provisioning With Guided Recovery}
One of the most common examples of how useful Nebula is in practical terms would be an error at the moment of a time-bound release, such as a deployment failing due to a permissions error in AWS, which is detected via Terraform. In a traditional case, the operator has to decipher the log output of the provider, determine what permissions are missing, access the IAM console separately and find out if the issue is related to credentials, scope, or regions.


In the case of Nebula, on the contrary, the operator would be presented with the record of the task completed with a status indicating a failure, the log output would be saved in one place, while the AI copilot will analyze the log and make suggestions as to why the deployment failed. Regardless of the accuracy of these recommendations, in most cases, narrowing down the search space will save additional time for the operator, which is crucial in stressful situations.


\section{Case Study: Inventory Drift Detection}


The other issue, which is common in any cloud provider's environment, is called inventory drift. It usually happens when resources are manually deleted via a provider portal or modified without following the automated deployment path. That leads to a situation when local inventory and real resources in the cloud have different state. With Nebula's periodic synchronization procedure, it is easier to bring the two back into agreement by reconciling provider state with the database.


In case a company works with several clouds simultaneously, such functionality will pay off many times over by providing accurate information about cloud estate in one central place.


\section{Organizational Benefits Beyond Provisioning}
The long-term value of a system like Nebula is not limited to provisioning speed. It also creates benefits in:
\begin{itemize}
    \item \textbf{training}: new engineers learn one operational workflow first,
    \item \textbf{documentation}: a single report or manual can describe cross-cloud actions consistently,
    \item \textbf{governance}: audit trails and approval patterns become easier to define,
    \item \textbf{support}: failures are easier to triage through centralized task records,
    \item \textbf{planning}: teams can compare provider choices from a shared interface.
\end{itemize}

\section{Limitations of Scenario-Based Evaluation}

The above examples are meant to be representative rather than exhaustive. Actual organizations might face other complications, such as different security boundaries, network topology issues, data privacy concerns, or procurement regulations that our academic prototype cannot account for. Nonetheless, we can draw several insights from analyzing these scenarios and relate them back to the design considerations in the earlier chapters

\section{Discussion}

The above scenarios demonstrate the primary claim made throughout this report. Multi-cloud operations are as much about orchestration and mental overhead as they are about connecting to cloud APIs. With its ability to consolidate intent and reduce operational fragmentation, Nebula helps achieve better productivity, better governance, and better reproducibility. In particular, it allows startups to get their feet wet more quickly, helps enterprises establish governance standards, and enables researchers and academics to conduct their work in a more systematic fashion.

\newpage
