% Chapter 9: Future Scope and Ethical Considerations
\chapter{FUTURE SCOPE AND ETHICAL CONSIDERATIONS}

The evolution of the cloud computing field means that the "Unified Command Center" paradigm defined by Nebula has laid out an initial groundwork for better orchestration techniques. The present setup has demonstrated that a reliable, asynchronous, and multicloud based control plane is possible. Now the key issue becomes what further developments could realistically build on the initial groundwork and what ethical considerations will need to be taken into account when defining such development paths. The future is not about just developing new functions, but also about how to behave when performing these functions.

\section{Future Research and Enhancements}
Though Nebula already provides management services for basic cloud infrastructure components such as virtual machines, storage, and networking primitives, its next significant step might be unification of the management of serverless computing functions. One "Nebula Function" should be able to provide all necessary resources needed for its deployment on platforms like AWS Lambda, Azure Functions, and Google Cloud Functions. The benefit from it will be especially high for those organizations that need regional redundancy without having separate deployment pipelines for each one.

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=2.0cm, auto, scale=0.82, every node/.style={scale=0.82}]
    \tikzstyle{core} = [rectangle, draw, rounded corners, fill=blue!10, text centered, minimum width=10em, minimum height=3em]
    \tikzstyle{future} = [rectangle, draw, rounded corners, fill=orange!10, text centered, minimum width=9em, minimum height=2.8em]
    \tikzstyle{line} = [draw, -latex']

    \node [core] (nebula) {Current Nebula Core};
    \node [future, above left=of nebula] (serverless) {Serverless Control};
    \node [future, above=of nebula] (dr) {Disaster Recovery};
    \node [future, above right=of nebula] (finops) {AI Cost Optimization};
    \node [future, below left=of nebula] (k8s) {Kubernetes Support};
    \node [future, below=of nebula] (policy) {Policy as Code};
    \node [future, below right=of nebula] (hybrid) {Hybrid / Edge Ops};

    \draw [line] (nebula) -- (serverless);
    \draw [line] (nebula) -- (dr);
    \draw [line] (nebula) -- (finops);
    \draw [line] (nebula) -- (k8s);
    \draw [line] (nebula) -- (policy);
    \draw [line] (nebula) -- (hybrid);
\end{tikzpicture}
\caption{Future Roadmap Dimensions for the Nebula Control Plane}
\label{fig:future_roadmap}
\end{figure}

\subsection{Serverless Cross-Cloud Orchestration (SaaS-less)}
While Nebula currently manages core infrastructure such as virtual machines, storage, and networking primitives, a major future expansion is unified management of serverless functions. A single "Nebula Function" could be expressed once and then translated into deployment artifacts for AWS Lambda, Azure Functions, and Google Cloud Functions. This capability would be especially valuable for teams that want regional resilience without maintaining multiple provider-specific deployment pipelines. A follow-up research problem here is how to normalize differences in trigger models, packaging constraints, timeout policies, and cold-start behavior across clouds without creating a misleading abstraction.

\subsection{Auto-Failover and Disaster Recovery (DR)}
The next more sophisticated one would be “Zero-Touch Failover.” In case of degradation of a whole region or even of an entire family of services, Nebula can launch Terraform plan that will reconstruct necessary infrastructure in an alternative provider/region altogether. This should be taken not as a guarantee of \(100\%\) uptime. Disaster Recovery entails tradeoffs when it comes to data freshness, DNS propaga- tion time, configuration divergence, and other legal issues. Thus, a serious Disaster Recovery system would include several levels of failover including cold site, warm site, and active-active site, among others. And Nebula, once again, would fit in perfectly since it already possesses the pro- visioning cycle process.

\subsection{AI-Powered Cost Optimization}
In terms of the current AI Copilot, its focus is failure analysis. In future iterations, it can extend to economic analysis through idle resource detection, burst profiling, storage capacity expansion, and compute underutilization detection. Instead of serving as an all-purpose chatbot, it can serve as a FinOps copilot that will explain why a workload is costly and how a different approach to deployment will lower costs. Examples of such advice would be to use spot-optimized regions for background tasks, replace overprovisioned virtual machine instances with optimal ones, and implement lifecycle management of rarely accessed objects.

\subsection{Kubernetes and Managed Container Platforms}
A related direction would involve having policies enforced prior to infrastruc- ture modifications. A policy engine would enforce region-based restrictions, mandatory tags, encryption requirements, naming standards, and network exposure policies. The end result would make Nebula more than an execution plane; it would be a control plane aware of governance concerns. From an academic perspective, policy enforcement actions would include logging along with reasons for enforcement, ensuring that when a user’s deployment fails, they know not only that it failed, but why.

\subsection{Policy-as-Code and Compliance Guardrails}
First, the capability provided by such an orchestration layer implies certain ethical obligations, which follow from the nature of the capabilities offered. Specifically, the orchestration layer enables one to provision, manipulate and destroy cloud resources on several clouds. In other words, the orchestration layer is anything but neutral in terms of ethical implications, and hence the degree of protection it offers should be considered an integral part of the layer’s ethics.

\subsection{Edge and Hybrid Resource Awareness}
Organizations do not exist solely within the confines of the public cloud. Branch offices, factory machinery, research environments, and private virtualization systems all play their roles. A mature Nebula implementation would eventually move into hy- brid and edge environments through integration with agents or connectors reporting on local infrastructure to fit into the same canonical inventory framework. While difficult, this approach is essential because it will test the control-plane abstrac- tions created in this project beyond the public cloud environment.

\section{Ethical and Security Considerations}
First, the capability provided by such an orchestration layer implies certain ethical obligations, which follow from the nature of the capabilities offered. Specifically, the orchestration layer enables one to provision, manipulate and destroy cloud resources on several clouds. In other words, the orchestration layer is anything but neutral in terms of ethical implications, and hence the degree of protection it offers should be considered an integral part of the layer’s ethics.

\subsection{Data Sovereignty and GDPR}
One of the most important ethical issues associated with using Nebula in the multi-cloud context relates to data residency. The application has to ensure that any sensitive information remains only in those geographic locations that are authorized. Simply putting the region option in the form of a dropdown menu does not help here since users may choose the wrong value. Instead, some geographic limitations should be embedded at the orchestration layer level, preventing the deployment of unauthorized plans.


\subsection{The Power of a Unified API}
Concentration of cloud access keys to one platform presents a high-value target for the attacker. Hence, the role of the developer ethically is to mitigate this risk of concentration. Runtime isolation, key rotation, use of credentials based on the principle of least privilege, log scrubbing, and audit trail are the ways of accomplishing it. It is imperative that the user knows which request action he made, what provider got affected, which credential and roles got impacted, etc.

\subsection{AI Explainability and Human Oversight}
In case the platform is equipped with artificial intelligence-driven recommendations, these recommendations must be explainable to the operator to make sure he has enough visibility to justify the applicability of such a recommendation. Any recommendation that cannot be justified from the log stream or by referring to a set of policies cannot be acted upon blindly by the operator. Failure scenarios are prone to this risk even more.


\subsection{Cost Fairness and Organizational Transparency}
The choice of cloud service providers and locations is not without organizational repercussions. An orchestration platform that prioritizes one vendor or location over another must disclose its decision-making process, which may include performance requirements, compliance issues, and cost considerations. In this context, ethical design implies transparency regarding the factors considered when making the decision.

\subsection{Environmental Sustainability}
Abstraction through cloud computing could unintentionally alienate cloud users from their responsibility to the environment. One possible improvement for the future would be a sustainability metric that can quantify the cost associated with over-provisioned, unused, or redundant infrastructure. Even though it will remain an estimate, it will bring users' attention to the issue of energy consumption by the cloud infrastructure.

\section{Governance Guidelines for Responsible Operation}
In order to responsibly implement a platform such as Nebula, it is necessary to adhere to the following governance principles:
\begin{enumerate}
    \item \textbf{Approval boundaries}: destructive operations should require explicit confirmation or policy approval.
    \item \textbf{Least privilege}:  credentials for providers should be limited only to the resources and activities that are necessary.
    \item \textbf{Auditable actions}: every provisioning, deletion, and remediation event should be attributable to a user or automation identity.
    \item \textbf{Policy transparency}: enforcement rules should be documented and visible to operators.
    \item \textbf{Human-in-the-loop AI}: automated suggestions should remain reviewable before irreversible changes occur.
\end{enumerate}

\newpage
% Chapter 10: Deployment and Operations Playbook
\chapter{DEPLOYMENT AND OPERATIONS PLAYBOOK}

The present chapter converts the system design into actionable steps. While the appendix user manual addresses itself to local configurations and usage, the present chapter deals with the environment architecture, release management, operational best practices, and support processes. An important practical question answered by the present chapter is how to maintain a reliable Nebula once it exists.

\section{Environment Topology}
The best way to operate \texttt{Nebula} is to do so in a multi-environment setup that has controlled environment promotions. The recommended base configuration includes:
\begin{itemize}
    \item \textbf{Local development}: individual developer machines using mocked/sandboxed credentials.
    \item \textbf{Shared integration}: an environment to test APIs/UI/worker compatibilities.
    \item \textbf{Staging}: a near-production configuration with realistic secrets management and sandbox clouds.
    \item \textbf{Production}: actual live control plane using authenticated operators.
\end{itemize}

Different database, broker, and encryption key usage should be maintained per environment.

\begin{figure}[H]
\centering
\begin{tikzpicture}[node distance=2.0cm, auto, scale=0.78, every node/.style={scale=0.78}]
    \tikzstyle{env} = [rectangle, draw, rounded corners, fill=green!10, text centered, minimum width=8em, minimum height=3em]
    \tikzstyle{line} = [draw, -latex']

    \node [env] (local) {Local Dev};
    \node [env, right=of local] (integration) {Shared Integration};
    \node [env, right=of integration] (staging) {Staging};
    \node [env, right=of staging] (production) {Production};

    \draw [line] (local) -- node[above] {merge / validate} (integration);
    \draw [line] (integration) -- node[above] {smoke tests} (staging);
    \draw [line] (staging) -- node[above] {manual approval} (production);
\end{tikzpicture}
\caption{Recommended Environment Promotion Flow for Nebula Deployments}
\label{fig:environment_promotion}
\end{figure}

\section{Release Pipeline}
The pipeline for code releases needs to have the following stages:

\begin{enumerate}
    \item static code validation of backend, frontend and Terraform files,
    \item unit testing of the validation code, API operations and utility functions,
    \item integration testing of queue workflow, data persistence to database,
    \item sandbox deployment using non-production cloud credentials,
    \item sandboxing with non-production credentials in cloud services provider environment,
    \item security review of release notes for any impact on security,
    \item gradual deployment to staging and production environments.
\end{enumerate}

\subsection{Illustrative CI/CD Flow}
\begin{lstlisting}[language=Python, caption=Release Pipeline Stages in Pseudo Workflow Form]
name: nebula-release
on:
  push:
    branches: [main]

jobs:
  validate:
    steps:
      - checkout
      - run backend lint
      - run frontend lint
      - run terraform validate

  test:
    steps:
      - run unit tests
      - run API contract tests
      - run queue integration tests

  package:
    steps:
      - build api image
      - build worker image
      - publish versioned artifacts

  deploy-staging:
    needs: [validate, test, package]
    steps:
      - apply staging configuration
      - run smoke tests

  approve-production:
    needs: [deploy-staging]
    steps:
      - manual approval

  deploy-production:
    needs: [approve-production]
    steps:
      - roll out api
      - roll out workers
      - verify health endpoints
\end{lstlisting}

\section{Operational Readiness Checklist}
Before enabling the platform for active user traffic, the following readiness checks should be completed:

\begin{table}[H]
\centering
\caption{Operational Readiness Checklist}
\label{tab:ops_readiness}
\begin{tabular}{|p{4.2cm}|p{2.2cm}|p{5.0cm}|}
\hline
\textbf{Control Item} & \textbf{Status Type} & \textbf{Expected Evidence} \\ \hline
API health endpoint & mandatory & returns HTTP 200 with version metadata \\ \hline
Worker queue connectivity & mandatory & successful enqueue and dequeue test \\ \hline
Database migrations & mandatory & schema version matches release tag \\ \hline
Secret injection & mandatory & runtime variables resolved without fallback defaults \\ \hline
Cloud sandbox credential test & recommended & read-only identity check passes for each provider \\ \hline
Audit logging & mandatory & create, delete, and login events persisted \\ \hline
Backup job verification & recommended & last successful snapshot within policy window \\ \hline
\end{tabular}
\end{table}

\section{Observability and Service Levels}
The operations team would require more information than logs from containers. In a good deployment, the system would output:
 

\begin{itemize}
    \item latency stats for APIs,
    \item throughput of workers and retries,
    \item failure reasons grouped by provider,
    \item time to reconciliation,
    \item trends in authentication failures,
    \item saturation of database connections,
    \item length of queue over time.
\end{itemize}

Based on all this data, we can construct some basic SLO framework. For instance, interactive API calls need to have low latency, queue tasks need to be executed with certain guarantees, and failing tasks must provide an explainable reason. All this is achievable and relevant for SLOs in control plane applications.

\section{Backup, Recovery, and Rollback}
Furthermore, production operations require recovery plans. The following items would need protection:





\begin{enumerate}
    \item the PostgreSQL database state - users, roles, resources and task info,
    \item configuration files and templates for Terraform modules,
    \item images and releases,
    \item logs and other operational data used in debugging.
\end{enumerate}

Rollbacks need special handling at each layer. Rollback in applications could entail rolling back the API and workers back to an earlier image. Rollback in databases can be tricky since it involves making forward changes instead of backwards ones.

In addition, Terraform rollbacks can be difficult since the infrastructure state has possibly been modified. Therefore, the best way to do a deployment is through progressive releases accompanied by smoke tests rather than large production releases.

\section{Incident Handling Model}
In the case of a user impact incident, the following needs to happen:
 




document remediation steps and post-incident actions.

\begin{enumerate}
    \item Classify the incident as either authentication problem,
    \item provider outage, queues, database issues, or application regression.
    \item Determine whether the blast radius involves single users, providers, or the entire system.
    \item Collect diagnostic information like task logs and recent configuration changes.
    \item Stabilize the system through halting any dangerous automations.
    \item Communicate with users on the situation.
    \item Document remediation steps and post-incident actions.
\end{enumerate}

\subsection{Example Runbook Entry}
\begin{table}[H]
\centering
\caption{Sample Incident Runbook}
\label{tab:incident_runbook}
\begin{tabular}{|p{3.0cm}|p{4.0cm}|p{4.4cm}|}
\hline
\textbf{Incident Type} & \textbf{Immediate Action} & \textbf{Follow-up Action} \\ \hline
Queue backlog & scale workers, inspect stuck tasks & tune retry policy and concurrency \\ \hline
Credential decrypt failure & stop execution for affected tenant & rotate key material and re-encrypt secrets \\ \hline
Provider API throttling & enable backoff and reduce fan-out & review sync scheduling policy \\ \hline
Database saturation & shed non-critical jobs & optimize queries and add pooling controls \\ \hline
\end{tabular}
\end{table}

\section{Change Management and Team Workflow}
Running a multi-cloud control plane requires diligent change management because any bug could impact more than one cloud provider simultaneously. Therefore, the following distinctions must be made when managing changes in software:

\begin{itemize}
    \item \textbf{feature changes}, that introduce new capabilities, like new resource types,
    \item \textbf{operation changes}, that include changes to logging, retry,
    \item \textbf{security releases}, concurrency, and observability,
    \item \textbf{security changes}, including anything involving authentication, credentials, and provider permissions.
\end{itemize}

The differences are important for planning how much review and testing is needed. For instance, changes to the retry scheduler should lead to stress testing, while changes to credentials should involve thorough security reviews.

\section{Why This Playbook Matters}
A lot of student projects usually end up with architectural diagram analysis and source code description. In practice, however, operational discipline will decide on survival of architecture when faced with real users. This chapter goes further than that contribution of the blackbook as it demonstrates that the platform was evaluated not only as an implementation task, but also as a service to be operated and improved upon. 

\newpage
