% Chapter 3: System Analysis (Massive Expansion)
\chapter{SYSTEM ANALYSIS}

Any multi-cloud project will be successful or not based on the quality of the Prob- lem Space analysis before moving to the Solution Space. This chapter outlines the technical requirements, limitations and the strategic planning of the Nebula platform.

\section{Software Requirements Specification (SRS)}
We divided our requirements in terms of IEEE-830 standard [29] into non-functional and functional goals.

\subsection{Actor Definitions}
1. \textbf{Cloud Administrator}: Adds cloud credentials and administers access to the organization. \\
2. \textbf{DevOps Engineer}: The primary user that provisions, administers and oversees resources in clouds. \\
3. \textbf{System Auditor}: Checks the cost reports and inventory history to check compliance.

\subsection{Use Case Descriptions}
The interactions between actors and the system to achieve special busi- ness objectives are detailed use cases.

\begin{itemize}
    \item \textbf{Use Case 1: Secure Credential Registration}
        \begin{enumerate}
            \item Registering Secure Credential. User clicks Register Provider, and enters an Access Key and Secret Key.
            \item The format is validated by the Pydantic schemas [30] by the system.\cite{pydantic_docs}.
            \item Key encryption with AES-128 and storage in PostgreSQL are done in the backend.
            \item The user is redirected to the “Settings" dashboard.
        \end{enumerate}
    \item \textbf{Use Case 2: Multi-Cloud VM Provisioning}
        \begin{enumerate}
            \item User clicks "New VM" and selects "AWS" as the provider.
            \item System obtains the pre-defined EC2 Terraform module.
            \item User is prompted to input instance name, size and region.
            \item System triggers a Celery task and gives a real-time status report.
        \end{enumerate}
\end{itemize}

\section{Requirement Traceability Matrix (RTM)}
The RTM is a document which maps and tracks user requirement with test cases. It also documents all the requirements suggested by the client and traceability of requirements in one document, at the end of the Software development life cycle. 

\begin{table}[H]
\centering
\caption{Requirement Traceability Matrix}
\label{tab:rtm}
\begin{tabular}{|p{1.5cm}|p{4.5cm}|p{3.5cm}|p{2cm}|}
\hline
\textbf{Req ID} & \textbf{Requirement Description} & \textbf{Design Ref} & \textbf{Test ID} \\ \hline
FR-01 & User Authentication via JWT & Sec-Arch 4.5 & TC-01 \\ \hline
FR-02 & Encrypted Credential Vault & Sec-Arch 4.5 & TC-02 \\ \hline
FR-03 & AWS Resource Provisioning & Engine 5.3 & TC-03 \\ \hline
FR-04 & Azure Resource Provisioning & Engine 5.3 & TC-04 \\ \hline
FR-05 & GCP Resource Provisioning & Engine 5.3 & TC-05 \\ \hline
FR-06 & AI Log Remediation Engine & AI-Logic 8.1 & TC-06 \\ \hline
FR-07 & Real-time Status Sync & Sync-Arch 4.6 & TC-07 \\ \hline
NFR-01 & Encryption at Rest (AES-128) & Sec-Arch 4.5 & TC-14 \\ \hline
NFR-02 & API Latency < 1s & HLD 4.1 & TC-33 \\ \hline
NFR-03 & System Uptime 99.9\% & Ops-Manual & TC-35 \\ \hline
\end{tabular}
\end{table}

\section{Detailed Project Schedule (16-Week Plan)}
The project was executed following a structured timeline, ensuring that every phase of the SThe project was conducted in a logical sequential manner and each SDLC stage was accorded sufficient time to conduct research, design, implementation and testing.

\subsection{Phase 1: Research and Feasibility (Weeks 1-3)}
- Multi-cloud gaps identification.
- Survey of 10 or more cloud tools (as discussed in Chapter 2). 
- Terraform as the orchestration engine validation.

\subsection{Phase 2: System Architecture Design (Weeks 4-6)}
- High-Level Design (HLD) formalization.
- Choice of tech stack: FastAPI, React, PostgreSQL, Redis and Celery.
- Database schema design and entity definition.

\subsection{Phase 3: Core Module Implementation (Weeks 7-11)}
- Nebula Vault credential security: Creating the Nebula Vault.
- Terraform Task Runner: Creating the Terraform Task Runner. 
- provider-specific HCL (AWS, Azure, GCP): Building modules.

\subsection{Phase 4: Frontend Development (Weeks 12-14)}
- Dashboard-based command center.
- Backend WebSock- ets-implemented real time stream logging.
- Copilot UI implementation.

\subsection{Phase 5: Testing and Deployment (Weeks 15-16)}
- Non- Functional and Functional testing (read Chapter 6).
- Final documentation and writing user manual.

\section{Risk Management and Mitigation}
The problem presents various threats that have already been discovered and dealt with in the analysis stage when a large number of cloud providers are involved.

\begin{table}[H]
\centering
\caption{Project Risk Matrix}
\label{tab:risk_matrix}
\begin{tabular}{|p{3cm}|p{1.5cm}|p{4.5cm}|p{3.5cm}|}
\hline
\textbf{Risk} & \textbf{Impact} & \textbf{Mitigation Strategy} & \textbf{Contingency} \\ \hline
Cloud API Rate Limiting & High & Implement exponential backoff in sync tasks. & Alert administrator. \\ \hline
Credential Compromise & Critical & Encryption at application layer (AES-128). & Secret rotation policy. \\ \hline
Terraform State Corruption & High & Use local backups and isolation per resource. & State recovery tools. \\ \hline
AI Hallucination & Medium & Sanitized logs and human-in-the-loop validation. & Fallback to raw logs. \\ \hline
Provider Outage & High & Multi-cloud redundancy (Nebula survives if 1 cloud fails). & Failover to other cloud. \\ \hline
\end{tabular}
\end{table}

\section{Data Dictionary for Core Entities}
The following table describes the characteristics of all the objects of operations in the PostgreSQL schema.

\begin{table}[H]
\centering
\caption{Nebula Data Dictionary}
\label{tab:dictionary}
\begin{tabular}{|l|l|l|l|}
\hline
\textbf{Entity} & \textbf{Attribute} & \textbf{Type} & \textbf{Description} \\ \hline
Credential & provider\_type & Enum & AWS, AZURE, or GCP \\ \hline
Credential & access\_key & String (Enc) & Encrypted primary access key \\ \hline
Resource & provider\_id & String & Unique cloud ID (e.g., i-12345) \\ \hline
Resource & status & Enum & active, pending, failed, or deleted \\ \hline
Task & execution\_log & Text & Full STDOUT/STDERR from Terraform \\ \hline
\end{tabular}
\end{table}

\newpage
