\documentclass[11pt,conference,onecolumn]{IEEEtran}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}

\title{Democratizing AWS Cloud Operations: A Unified Orchestration Approach to Standardized Infrastructure Management\\
{\footnotesize \textsuperscript{*}An Implementation-Driven Study with Nebula}
}

\author{\IEEEauthorblockN{Priyanshu Kumar Sharma, Vaishnavi Jadhav, Vaibhav Gulage}
\IEEEauthorblockA{\textit{Computer Engineering Department} \\
\textit{Ajeenkya D Y Patil University}\\
priyanshu17ks@gmail.com}
}

\maketitle

\begin{abstract}
Cloud adoption has accelerated faster than operational standardization, creating a persistent gap between infrastructure capability and manageability. This paper addresses search gaps with \textit{Nebula}, an implementation-driven AWS orchestration platform that consolidates provisioning, inventory synchronization, monitoring, and cost visibility into a single control surface. The system utilizes React, FastAPI, PostgreSQL, Celery, and Terraform to achieve infrastructure reproducibility. The study demonstrates how a layered orchestration model decouples user-facing workflows from long-running cloud operations while preserving traceability. Empirical results derived from our AWS implementation show 25 tracked resources, 145 ms provider-health latency, and sub-100 ms API acknowledgement under concurrent load. These findings indicate that standardized cloud operations are achievable without sacrificing responsiveness. The approach establishes a defensible technical baseline for future multi-cloud expansion.
\end{abstract}

\begin{IEEEkeywords}
AWS orchestration, Infrastructure as Code, Terraform, Celery, cloud standardization, SaaS platform.
\end{IEEEkeywords}

\section{Introduction}
\input{sections/introduction}

\section{Background and Strategic Context}
\input{sections/literature_review}

\section{Strategic Value Proposition}
\input{sections/value_proposition}

\section{Key Features and AI Integration}
\input{sections/ai_integration}

\section{Implementation Details}
\input{sections/implementation}

\section{Performance Evaluation and Results}
\input{sections/performance}

\section{Deployment and Future Scope}
\input{sections/deployment}
\input{sections/future_work}

\section{Conclusion}
\input{sections/conclusion}

\section*{Acknowledgements}
The authors would like to thank the open-source community for the tools and frameworks that made this project possible.

\section*{Declarations}
\textbf{Conflicts of Interest:}\\
All authors declare that they have no conflicts of interest.

\textbf{Use of AI Technology:}\\
During the preparation of this work, the authors utilized AI technology (Google Gemini) to assist with structural formatting, proofreading, and the standardization of bibliographic references. After using this tool, the authors reviewed and edited the content as needed and take full responsibility for the accuracy and originality of the publication.

\textbf{Notes to the Editor:}\\
This manuscript describes the design and implementation of the \textit{Nebula} AWS orchestration platform. The authors confirm that this work is original and has not been submitted for publication elsewhere.

\bibliographystyle{IEEEtran}
\bibliography{references}

\end{document}
